---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)
library(tidyverse)

```

```{css}
@import url('https://fonts.googleapis.com/css2?family=Noto+Sans:ital,wght@0,100..900;1,100..900&display=swap');

body {
  font-family: 'Noto Sans', sans-serif;
}

h2 {
  color: #000000;
  background-color: #FFCBFC;
  padding: 10px;
  font-style: italic;
}

```

## My TikTok Themes and Behaviour

The data I've collected focuses on *my personal TikTok feed*, particularly during quick, **5-minute timed** scroll sessions. It reveals the trends in content pushed out to me in a short period of time, as well as my engagement behaviour relating to the amount of videos I consume in these short scroll sessions and whether the videos spark my interest or not.


```{r}
#Naming the URL of my published csv file
csv_file <- "https://docs.google.com/spreadsheets/d/e/2PACX-1vRD_dheONZxG4QxuWG3c2EVUYQga6SObr3XqU2agRTJla3EHx56Re8XrPvWibxqAiuCBkB6wLCPs2We/pub?gid=311737042&single=true&output=csv"

#reading my data and creating a data frame 
logged_data <- read_csv(csv_file)

#renaming my data variables to create a new data frame
latest_data <- read_csv(csv_file) %>%
  rename(total_videos_watched = 2,
         content_type = 3,
         engagement_type = 4,
         longest_watched_video = 5,
         shortest_watched_video = 6)

#informative bar graph for content type on TikTok
latest_data %>%
  ggplot() +
  geom_bar(aes(x = content_type),
           fill = "#CDB5CD") +
  labs(title = "Top watched content on TikTok",
       subtitle = "The most commonly viewed content on TikTok during my 5-minute timed scroll sessions",
       caption = "Source: Avani Narayan, TikTok Feed Survey - stats220",
       x = "Content type",
       y = "Number of scroll sessions (5-minute timed)")



#informative bar graph for engagement with videos on TikTok
latest_data %>%
  ggplot() +
  geom_bar(aes(x = engagement_type),
           fill = "#A2B5FF") +
  scale_x_discrete(labels = c("Mixed", 
                              "Mostly skipped", 
                              "Mostly watched fully")) +
  labs(title = "Engagement on TikTok",
       subtitle = "Comparing my engagement with TikTok videos during my 5-minute timed scroll sessions",
       caption = "Source: Avani Narayan, TikTok Feed Survey - stats220",
       x = "Engagement type",
       y = "Number of scroll sessions (5-minute timed)")



#the mean number of TikTok videos I watched in 5-minutes
mean_watched_vids <- round(latest_data$total_videos_watched %>% mean(), digits = 0)

#the longest video I encountered on TikTok (converted to minutes)
longest_vid <- round(latest_data$longest_watched_video %>% max() / 60, digits = 2)

#the shortest video I encountered on TikTok (kept in seconds)
shortest_vid <- latest_data$shortest_watched_video %>% min() %>% round(1)

paste0("The mean number of TikTok videos I watch in 5-minutes is ", mean_watched_vids, " videos. The longest video I've encountered on TikTok is ", longest_vid, " minutes long, and the shortest video I've encountered on TikTok is ", shortest_vid, " seconds long.")


```


